\documentclass[final-report.tex]{subfiles}

\begin{document}

% Based on the result, Discuss the potential future developments, opportunities, and challenges that FOSH is facing as well as identify the fields where we could focus more attention on FOSH.

As discussed above, FOSH itself is likely to be characterized by continued innovation and expansion, as well as a focus on developing more specialized and adaptable FOSH electronic platforms. With the continued development of FOSH platforms like Linux and Arduino. FOSH also has the potential to positively and significantly impact healthcare from many perspectives. In the future, we believe there will be continued development of affordable and accessible FOSH medical devices, aiming to reduce the cost to meet the needs of low-resource environments. In addition, rigorous quality standards and certification processes for FOSH medical devices will be established, which can further build consumer trust and confidence in these products. Given that operational products such as robot hands or detectors are not fully tested and matured yet, it is necessary for FOSH communities and healthcare professionals to collaborate and ensure their safety and effectiveness. This will effectively promote the integration of FOSH into healthcare systems.

As for the field of robotics and automation, there will be continued development of more advanced and sophisticated FOSH devices, including the most state-of-the-art integration of artificial intelligence and machine learning technologies, which will be continuously updated as technology advances. 

In the educational context, the increasing adoption of open-source hardware in academic institutions required that current contributors and developers of open-source hardware consider putting more attention to the FOSH documentation and user interfaces. By making these resources more accessible and user-friendly, novice users, such as students, can more readily engage with the material and acquire foundational knowledge of open-source hardware principles. This approach will ultimately foster interest in hardware development and facilitate the learning process for those new to the field.

Additionally, in order to make the FOSH community more collaborative, we also encourage hardware contributors to follow the principles from industry and academia which will motivate further open-source hardware developers' participation. 


\end{document}